Euler's polyhedron formula

### 2016-02-25 mandatory_assignment/main.tex
spelling mistakes

\begin{definition}[Polyhedron]
    A \emph{polyhedron} is a solid in three dimensions with flat polygonal
    faces, straight edges and sharp corners or vertices.\footnote{This
    definition is not very precice, but it will suffice for our purposes.}
\end{definition}

Polyhedra are named based on the number of faces using the greek prefix system.
Some examples include the \emph{hexahedron}, otherwise known as the cube with
its six faces; the \emph{octahedron} or \emph{double pyramid} with its eight
faces; and the \emph{icosahedron} with its 20 faces.

@@

Direct applications of the polyhedron formula can be hard to find. However, its
generalizations to other mathematical fields as topology gives us an indication
as to what kind of topological object we are working with. The \emph{euler
characteristic}, denoted $\chi$, is a topological invariant. In this more
general sense, our polyhedron formula reads $\chi = V - E + F$, where $\chi =
2$. This characteristic can for instance be used to classifly the platonic
solids. \cite{chi} presents a lot of mathematical results using the euler
characteristic.

>>>>

\begin{definition}[Polyhedron]
    A \emph{polyhedron} is a solid in three dimensions with flat polygonal
    faces, straight edges and sharp corners or vertices.\footnote{This
    definition is not very precise, but it will suffice for our purposes.}
\end{definition}

Polyhedra are named based on the number of faces using the Greek prefix system.
Some examples include the \emph{hexahedron}, otherwise known as the cube with
its six faces; the \emph{octahedron} or \emph{double pyramid} with its eight
faces; and the \emph{icosahedron} with its 20 faces.

@@

Direct applications of the polyhedron formula can be hard to find. However, its
generalizations to other mathematical fields as topology gives us an indication
as to what kind of topological object we are working with. The \emph{euler
characteristic}, denoted $\chi$, is a topological invariant. In this more
general sense, our polyhedron formula reads $\chi = V - E + F$, where $\chi =
2$. This characteristic can for instance be used to classify the platonic
solids. \cite{chi} presents a lot of mathematical results using the Euler
characteristic.
